Robust self-testing of large entanglement with constant alphabet

### 2019-04-22 Draft/draft.tex
Honghao: rewrote section 2

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}

@@

\title{Self-test prime dimensional EPR pairs with constant alphabet}

@@

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
\textbf{Notations}.
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
The maximally entangled state of local dimension $d-1$ for some prime $d$ is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
We denote a Hilbert space by $\calH$. Note that we only work with finite Hilbert spaces in this work.
When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
$\calH_B$.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, the Pauli operators
are defined by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}

For quantum states and operators on different Hilbert spaces, we use subscripts to label them.
For example, $O_A$ is an operator on Alice's side and $\ket{0}_{B}$ is a state on Bob's side. 
The only exception is for projectors used in a quantum strategy defined below, where the subscript 
is the input and the superscript is the output. For example, $A_x^a$ is Alice's projector for input $x$ and output $a$.
Operators defined by the projectors follow the same convention. For example, $A_x := A_x^0 - A_x^1$.

We use the following notation for the closeness between states.
\begin{align}
	\ket{u} \appd{\epsilon} \ket{v} \iff \norm{\ket{u} - \ket{v}} \leq \epsilon. 
\end{align}
Similarly, for $a,b \in \C$, we have
$a \appd{\epsilon} b \iff \norm{a-b} \leq \epsilon$.

\textbf{Number theory}.
We use some basic number theory in our work. A primitive root of a prime number
$d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
in the multiplicative group of integers modulo $d$, $\Zd$. Equivalently,
$r$ is the generator of $\Zd$.

%We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
%\begin{align}
%	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
%\end{align}
%where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
%and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
%definitions and notation for now.}
%Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
%unless otherwise specified, for example, the $k/r$ above.

\textbf{Nonlocal games}. 
The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0,1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new result.

A quantum strategy of a nonlocal game consists of projective measurements $\{\{A_x^a\}_a\}_x$ on Alice's side, 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
the condition that $P^2 = P = P\ct$.  \carl{You need to put explicit labels on the quantum systems used by
Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
\hf{Addressed in the notation part. --H.F}
Then Alice and Bob's quantum strategy produces the correlation
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.

\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$. 
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.  \carl{Make this clear in the definition itself.}
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of observables for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectrum decompositions of the observables.

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,c) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,c)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
the linear system game ($Hx = c$) is given by 
\begin{enumerate}
	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$,
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
We follow a similar approach to construct our ideal strategy. However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, $\calX = \calY = \{1, 2\}$ and $\calA = \calB = \{0,1\}$.
We define binary observables $A_x := A_x^0 - A_x^1$ and $B_y := B_y^0 - B_y^1$ from Alice and Bob's projectors.
It is easy to see that the binary observables are Hermitian and their only eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y} := \bra{\psi} A_x B_y \ket{\psi}$ is the expectation value of of the observables. 
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements up to isometry, 
which is a phenomenon referred as a self-test.
We give the definition of a self-test below and the
formal statement of this self-testing property of $\I_\alpha$. in \cref{sec:chsh}.

@@

\carl{Before the next definition, you should define what a ``correlation'' is.}
\hf{Mentioned in the nonlocal game part, but not sure how to make it a definition. --HF}
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}

>>>>

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}

@@

\title{Robust self-testing of large entanglement with constant alphabet}

@@

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we are interested in is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
We denote a Hilbert space by $\calH$. Note that we only work with finite Hilbert spaces in this work.
When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
$\calH_B$.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
the maximally entangled state is denoted by 
\begin{align}
	\ket{\EPR{2}} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are given by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}

For quantum states and operators on different Hilbert spaces, we use subscripts to label them.
For example, $O_A$ is an operator on Alice's side and $\ket{0}_{B}$ is a state on Bob's side. 
The only exception is for projectors used in a quantum strategy defined below, where the subscript 
is the input and the superscript is the output. For example, $M_x^a$ is Alice's projector for input $x$ and output $a$.
Operators defined by the projectors follow the same convention, for example, $M_x := M_x^0 - M_x^1$.

We use the following notation for the closeness between quantum states.
\begin{align}
	\ket{u} \appd{\epsilon} \ket{v} \iff \norm{\ket{u} - \ket{v}} \leq \epsilon. 
\end{align}
Similarly, for numbers $a,b \in \C$, the closeness is denoted by
$a \appd{\epsilon} b \iff \norm{a-b} \leq \epsilon$.

We use some basic number theory in our work. 
\begin{definition}
A primitive root of a prime number
$d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
in the multiplicative group of integers modulo $d$, $\Zd$.
\end{definition}
In other words,
$r$ is the generator of $\Zd$.

%We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
%\begin{align}
%	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
%\end{align}
%where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
%and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
%definitions and notation for now.}
%Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
%unless otherwise specified, for example, the $k/r$ above.
%-----------------------------------------
\subsection{Nonlocal games}
%-----------------------------------------
In a nonlocal game, there are two players, Alice and Bob and each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and her answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. 
Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0,1\}$ which corresponds to losing and winning. 
Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy beforehand.

A quantum strategy of a nonlocal game presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
\carl{You need to put explicit labels on the quantum systems used by
Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
\hf{Addressed in the notation part. --H.F}
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
\carl{Make this clear in the definition itself.}
\hf{I made the definition of the scoring function part of the big definition now.}
In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables.

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
the finite-dimensional representation of a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,\uc) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
the linear system game ($H\ux = \uc$) has
\begin{enumerate}
	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$,
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
We follow a similar approach to construct our ideal strategy. However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.

%-------------------------------------------------------------------------------
\subsection{The weighted CHSH inequality \cite{acin2012}.}
%-------------------------------------------------------------------------------
The weighted CHSH inequality is extracted from the CHSH test, which is another nonlocal game. 
The input sets and output sets of Alice and Bob are
$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
The scoring function for the $\alpha$-weighted CHSH test is defined by
\begin{align}
	V(a,b,x,y)_{\alpha-CHSH} = 
	\begin{cases}
		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
	\end{cases}
\end{align}
Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
The weighted CHSH inequality states that 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2\alpha,
\end{align}
where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of of the observables. 
The weighted CHSH inequality is true 
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
However, If they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
\begin{align}
\label{eq:chsh_max}
 \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
	consists of the joint state $\ket{\EPR{2}}$ and observables $M_1 = \pauliz$, $M_2 = \paulix$,
	$N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
strategy up to some local isometry, 
which is a phenomenon referred as a robust self-test.
We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.

@@

\carl{Before the next definition, you should define what a ``correlation'' is.}
\hf{Done. I decided to remove the definition of self-testing here because I think it is hard
to give a general robust self-testing definition and it suffices to just give our robust self-testing result.}
%\begin{definition}[Self-testing]
%	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
%	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
%	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
%	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
%	such that 	
%	\begin{align*}
%		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
%	\end{align*}
%\end{definition}
